---
title: "diagnosis_QQplot"
author: "chj1ar"
date: "2019-08-12"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
# Goal
Diagnose whether there are too few eQTL SNPs in the eQTL PIP data.

# Background
As the result of the enrichment analysis using eQTL PIP data showed, the credible intervals of $\alpha_1$ were too large, suggesting that there were probably too few eQTL SNPs.

# Methods
Select the SNPs whose eQTL PIPs are more than a pre-specified PIP threshold as the eQTL SNPs. Select all SNPs in the GWAS data as the full GWAS. For each set of selected SNPs, draw a QQ plot of log(GWAS P-values) of the SNPs (i.e., Observed log(GWAS P-values)) vs. log(GWAS P-values) where P-values follow the standard uniform distribution (i.e., Expected log(GWAS P-values)). Then visually compare the 2 QQ plots. If the 2 curves are very close, then there are too few eQTL SNPs.

# Input
GWAS data, eQTL PIP data

# Output
QQ plots: Observed log(GWAS P-values) vs. Expected log(GWAS P-values)

# Results
```{r, echo=FALSE}
library(png)
QQplot_P20fullGWAS <- readPNG(source = '~/Documents/留学/暑研/Xin/reading_materials/5th/QQplot_P20_fullGWAS.png')
library(grid)
grid.raster(QQplot_P20fullGWAS)
```

Figure 1: the QQ plot of P-values of brain eQTL SNPs with PIP > 0.2 in at least one brain tissue (blue) vs. full GWAS SNPs (black).

It is evident that there are few SNPs enriched in brain eQTLs, indicating little enrichment of brain eQTLs.

Also, almost all GWAS hits are not brain eQTLs, which is reasonable though. Briefly speaking, gene expression is just one aspect for SCZ, and there are other aspects like protein production, various modifications, and stages like infants and adults.

In addition, the most significant eQTL SNPs, defined as PIP > 0.5 in at least one brain tissue, are not so significant GWAS hits, and on the other hand, some less significant eQTL SNPs, such as those with PIP between 0.2 and 0.5, are significant GWAS hits, shown in Figure 2.

```{r, echo=FALSE}
library(png)
QQplot_P50P20 <- readPNG(source = '~/Documents/留学/暑研/Xin/reading_materials/5th/QQplot_P50_P20.png')
library(grid)
grid.raster(QQplot_P50P20)
```

Figure 2: the QQ plot of P-values of brain eQTL SNPs with PIP > 0.5 (orange) and PIP > 0.2 (blue) in at least one brain tissue.

